---
title: "sokol"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sokol}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Goal - Estimate the relative transmissivity change or head


### Transmissivity solution

Given (Sokol eq 6):
The example will be a single unit where we add a new one.

$$h_w = \frac{T_1 H_1}{T_1}$$
$$h_w + \Delta h_w = \frac{T_1 H_1 + T_2 H_2}{T_1 + T_2}$$

where:

- $h_w$ is the blended head for the shorter interval
- $h_w + \Delta h_w$ is the blended head for the larger interval
- $T_1$ is the transmissivity for the shorter interval
- $T_1 + T_2$ is the transmissivity for the larger interval
- $H_2$ is the head corresponding to the $T_2$ interval


Multiply denominators:

$$h_w T_1 = T_1 H_1$$
$$h_w T_1 + h_w T_2 + \Delta h_w T_1 + \Delta h_w T_2 = T_1 H_1 + T_2 H_2$$

Subtract first from second:

$$h_w T_2 + \Delta h_w T_1 + \Delta h_w T_2 = T_2 H_2$$

Put $T_2$ on one side:
$$\Delta h_w T_1 = T_2 H_2 - h_w T_2 - \Delta h_w T_2$$

Rearrange:
$$\frac{\Delta h_w T_1}{H_2 - h_w - \Delta h_w} = T_2$$

$T_2$ is now in terms of known values


### Head solution

Start from the previous proof: 
$$h_w T_2 + \Delta h_w T_1 + \Delta h_w T_2 = T_2 H_2$$

Rearrange:
$$H_2 = \frac{h_w T_2 + \Delta h_w T_1 + \Delta h_w T_2}{T_2}$$



## Examples
Can we recover missing values?  In this example we test if we can recover the missing value for the $10^th$ interval.

```{r setup, fig.width = 7, fig.height = 5}

library(sokol)

set.seed(123)
transmissivity <- abs(rnorm(10))
head <- sort(rnorm(10))
plot_blended(transmissivity, head)
blended_1 <- estimate_blended_head(transmissivity[1:9], head[1:9])
blended_2 <- estimate_blended_head(transmissivity, head)
estimate_missing(blended_2, 
                 c(transmissivity),
                 c(head[1:9], NA_real_))
head[10]

estimate_missing(blended_2, 
                 c(transmissivity[1:9], NA_real_),
                 c(head))
transmissivity[10]

```
